Fusion Moves for Correlation Clustering

### 2014-11-14 paper/egpaper_for_review.tex
fixed all changes including page 5

\noindent \textbf{Randomized Watersheds (RWS):}
%\subsubsection{Randomized Watersheds (RWS)}
Watersheds have become quite popular for
graph segmentation and have a strong connection
to energy minimization~\cite{couprie_2011}.
%
The edge weighted watershed algorithm~\cite{meyer_2013}
with random seeds can be used to get
cheap proposals.
To improve \emph{quality} we do not use $n$ seeds distributed uniformly
over all nodes but use the following.
%
We draw $n/2$ negative edges, and assign different seed to the endpoints
of each edge.
Doing so, a random subset of negative edges is forced
to be cut within each proposal.
For additional \emph{diversity}, noise $\mathcal{N} (0, \sigma_{ws})$
is added to the edge weighs.

@@

\section{Experiments}\label{sec:exp}
In our experiments we compare to the following methods with public available implementation.
%
For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}{\url{github.com/opengm/opengm/tree/cgc-cvpr2014}}}
of Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{github.com/opengm/opengm}}.
For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we use an modified version of
 the public available implementation in OpenGM\footref{opengm-master} of Kappes~\etal, as described in Sec.~\ref{sec:tunedMC}.
%
%We realize that their implementation has some limitations on large problems and make the following modifications.
%Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
%Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
%during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
%This procedure is one magnitude faster, but might cause a few extra outer iterations.
%In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
%For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
%
From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
We use the public available code of Micha Elsner\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
While this implementation uses full adjacency matrixes it does not scale as well and can not be applied on all datasets.
We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
%
As reported in~\cite{beier_2014_cvpr}, CGC is faster and gives better energies then PlanarCC~\cite{yarkony_2012_eccv} and Expand \& Explore~\cite{bagon_2011_arxiv}.
Therefore we exclude those in our experiments.

We compare this methods to the following methods suggested in the present paper.
%
Energy Based Based Hierarchical Clustering (\textbf{EHC}),
as described in Sec.~\ref{sec:ehc}.
%
CGC warm started with the solution from EHC denoted by \textbf{EHC-CGC}.
%
The proposed correlation cluster fusion algorithm with EHC-based and watershed-based proposals
 and MC-I and CGC as subproblem solvers denoted by 
\textbf{CC-Fusion-HC-MC},
\textbf{-HC-CGC},
\textbf{-WS-MC}, and 
\textbf{-WS-CGC}, respectively.
We set the size of the proposals fix to $10\%$ of the original problem size
and use random edge noise with $\sigma=1.5$.
%
As stopping condition we choose $10^4$ iterations and $100$ iterations with no improvement.

All experiments were run on Intel Core i5-4570 CPUs
with 3.20 GHz, equipped with 32 GB of RAM.
In our evaluation we make not use of multiple threads.
The methods were stopped if they exceed 30 minutes at the next possible interrupt point.

>>>>

\noindent \textbf{Randomized Watersheds (RWS):}
%\subsubsection{Randomized Watersheds (RWS)}
Watersheds have become quite popular for
graph segmentation and have a strong connection
to energy minimization~\cite{couprie_2011}.
%
The edge weighted watershed algorithm~\cite{meyer_2013}
with random seeds can be used to get
cheap proposals.
To improve \emph{quality} we do not use $n$ seeds distributed uniformly
over all nodes but use the following.
%
We draw $n/2$ negative edges, and assign different seed to the endpoints
of each edge.
Doing so, a random subset of negative edges is forced
to be cut within each proposal.
For additional \emph{diversity}, noise $\mathcal{N} (0, \sigma_{ws})$
is added to the edge weighs \cite{straehle_2012}.

@@

\section{Experiments}\label{sec:exp}
In our experiments we compare to the following methods with publicly available implementation.
%
For \textbf{CGC}~\cite{beier_2014_cvpr} we used the publicly available implementation\footnote{\label{opengm-cvpr2014}{\url{github.com/opengm/opengm/tree/cgc-cvpr2014}}} and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{github.com/opengm/opengm}}.
For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we use a modified version of
 the publicly available implementation in OpenGM\footref{opengm-master}, as described in Sec.~\ref{sec:tunedMC}.
%
%We realize that their implementation has some limitations on large problems and make the following modifications.
%Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
%Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
%during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
%This procedure is one magnitude faster, but might cause a few extra outer iterations.
%In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
%For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
%
From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
We use the publicly available code\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
While this implementation uses full adjacency matrices it does not scale as well and can not be applied on all datasets.
We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
%
As reported in~\cite{beier_2014_cvpr}, CGC is faster and gives better energies than PlanarCC~\cite{yarkony_2012_eccv} and Expand \& Explore~\cite{bagon_2011_arxiv}.
Therefore we exclude those in our experiments.

We compare these methods to the following methods suggested in the present paper.
%
Energy Based Based Hierarchical Clustering (\textbf{EHC}),
as described in Sec.~\ref{sec:ehc}.
%
CGC warm started with the solution from EHC denoted by \textbf{EHC-CGC}.
%
The proposed correlation cluster fusion algorithm with EHC-based and watershed-based proposals
 and MC-I and CGC as subproblem solvers denoted by 
\textbf{CC-Fusion-HC-MC},
\textbf{-HC-CGC},
\textbf{-WS-MC}, and 
\textbf{-WS-CGC}, respectively.
We set the size of the proposals to $10\%$ of the original problem size
and use random edge noise with $\sigma=1.5$.
%
As stopping condition we choose $10^4$ iterations and $100$ iterations with no improvement.

All experiments were run on Intel Core i5-4570 CPUs
with 3.20 GHz, equipped with 32 GB of RAM.
In our evaluation we make no use of multiple threads.
The methods were stopped if they exceed 30 minutes at the next possible interrupt point.
